Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-09 paper.tex
First draft of 'Growable' section.

\subsection{Narrative Interface}

@@

% not always a story -- kid can draw on their own and return to the
% story; Nell will observe the free play and offer suggestions.
\subsection{Personalization}
% customization, renaming characters

@@

\subsection{Direct interaction}
% constructionist?
% handwriting as UI?
% motor skills
% photo of XO-3?

\subsection{Growable (``no ceiling'')}
% it has a ``low floor and no ceiling'' to allow a child to master more
% and more of the system as she grows.

% modular -- the story expands.
% excerpt of TurtleScript
% text read aloud initially

\section{Technology}
\subsection{Rule-based story modules}
% excerpt of story model
% rete algorithm, cite Riedl, etc.
% programmable conflict resolution
\subsection{Simple dialog with AIML}
% eliza interactions, show fragment
\subsection{Web technologies}
% Javascript/HTML5
% offline caching
% turtles (almost) all the way down (turtlescript again)

>>>>

\subsection{Narrative}

@@

% not always a story -- kid can draw on their own and return to the
% story; Nell will observe the free play and offer suggestions.
\subsection{Personalized}
% customization, renaming characters

@@

\subsection{Growable}
The Nell system aims to have a ``low floor and no ceiling.''  The low
floor is a very simple base system, usable with no literacy skills or
external guidance.  The system then grows with the child's expanding
capabilities, serially accumulating story modules to tackle topics of
increasing difficulty.  As mentioned before, the ability for third
parties to independently author story modules is necessary to ensure
Nell can continue to grow.  There should be no external dependencies
limiting a child's ability to participate in this process: a Nell
system should contain a story editor and everything necessary to
author and publish story modules.

We also seek to eliminate the ``ceiling'' between the children and
the authors of the Nell system itself.  Nell should be capable of
teaching about itself, and a capable child can dive into Nell's source
code and make meaningful changes.  In section~\ref{sec:turtles} we
describe how this goal is approached.

% it has a ``low floor and no ceiling'' to allow a child to master more
% and more of the system as she grows.
% modular -- the story expands.
% text read aloud initially

\subsection{Direct interaction}
% constructionist?
% handwriting as UI?
% motor skills
% photo of XO-3?
The Nell system is tied to its implementation on a tablet computer.
It's no accident that the Nell system is instantiated on a tablet.
XXX

\section{Technology}
\subsection{Rule-based story modules}
% excerpt of story model
% rete algorithm, cite Riedl, etc.
% programmable conflict resolution
\subsection{Simple dialog with AIML}
% eliza interactions, show fragment
\subsection{Web technologies}\label{sec:turtles}
% Javascript/HTML5
% offline caching
% turtles (almost) all the way down (turtlescript again)
% excerpt of TurtleScript
